% !TEX root = ../main.tex

\chapter*{Acknowledgments}

First and foremost, I would like to express my sincere gratitude to my advisor and mentor, Dr. Jeremy Clark, for his help and guidance throughout my master's studies. He recruited me as a research assistant in the second semester of my study and led me to the world of blockchain and applied cryptography. I started my research in zero-knowledge proofs as a person who has shallow understanding in this area, but he has been always available to answer my questions and provide valuable feedback. I am impressed by his extensive knowledge and expertise in blockchain and cryptography. More importantly, he is also a friend offering a listening ear when I shared my experience and thoughts while living abroad. Simply put, he is the best advisor I could have ever asked for, and I know I can always count on him.

Secondly, I am deeply grateful to my lovely wife, Yun, for her accompany and support during my studies. I could not have succeeded to pursue a graduate degree abroad without her encouragement and understanding. She has been always there whenever I need her, especially for her comfort and care when I was ill. We have visited many great places in Canada and she made our journey colourful and memorable. I am also thankful to my parents for their support and love, helping me grow from a small child into a responsible adult.

I also want to thank all the mentors, friends, and even strangers who helped me for my academic career, including Dr. Benoît Dupont, Dr. Junda Liu, and Dr. Binyi Chen. I would not become a researcher without their mentorship.

Finally, I would like to thank Dr. Amr Youssef and Dr. Gengrui Zhang for serving on my thesis committee and for their time and effort to review my thesis and provide valuable comments.
